Figures

### 2019-12-03 manuscript/figures.Rmd
caption fix

```{r tn_re_compare-1, fig.cap = "Histograms showing the distribution of Clay and N deposition for the corn sensitive regions compared to all other regions. Medians for each group are shown as vertical dashed lines.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/tn_re_compare-1.pdf")
```

>>>>

```{r tn_re_compare-1, fig.cap = "Histograms showing the distribution of Clay for regions sensitive to watershed land-use (see highlighted credible intervals in Figure 4) relative to all other regions. Medians for each group are shown as vertical dashed lines.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/tn_re_compare-1.pdf")
```
